\documentclass[14pt]{extarticle}
\usepackage[a4paper,margin=2cm]{geometry}

\usepackage{fontspec}
\setmainfont{Gentium Plus}

\usepackage{gb4e}
\newcommand{\SG}{\textsc{sg}}
\newcommand{\M}{\textsc{m}}
\newcommand{\F}{\textsc{f}}
\newcommand{\PROSP}{\textsc{prosp}}
\newcommand{\SBJ}{\textsc{sbj}}
\newcommand{\OBJ}{\textsc{obj}}
\newcommand{\GEN}{\textsc{gen}}
\newcommand{\AOR}{\textsc{aor}}
\newcommand{\PRET}{\textsc{pret}}

\begin{document}

\begin{exe}
\ex
\gll aməd̥ːukəl inux, i-mːud utʃu.\\
friend:{\SG} 1{\SG}.{\GEN} 3{\SG}.{\M}.{\SBJ}-prepare.{\PRET} couscous\\
\glt `My friend prepared the couscous.'

\ex
\gll mːud-x utʃu.\\
prepare.{\PRET}-1{\SG}.{\SBJ} couscous\\
\glt `I prepared the couscous.'

\ex
\gll ad i-mːud utʃu.\\
{\PROSP} 3{\SG}.{\M}.{\SBJ}-prepare.{\AOR} couscous\\
\glt `He will prepare the couscous.'

\ex
\gll aməd̥ːukəl inux, mani i-mːud utʃu?\\
friend:{\SG} 1{\SG}.{\GEN} where 3{\SG}.{\M}.{\SBJ}-prepare.{\PRET} couscous\\
\glt `Where did my friend prepare the couscous?'

\ex
\gll mani ala i-mːud utʃu.\\
where {\PROSP} 3{\SG}.{\M}.{\SBJ}-prepare.{\AOR} couscous\\
\glt `Where will he prepare the couscous?'

\ex
\gll mani ala fːr-əx taʒrˁa?\\
where {\PROSP} hide.{\AOR}-1{\SG}.{\SBJ} dish\\
\glt `Where shall I hide the dish?'

\ex
\gll a sː mːud-əx.\\
{\PROSP} 3{\SG}.{\M}.{\OBJ} prepare.{\AOR}-1{\SG}.{\SBJ}\\
\glt `I will prepare him/it.'

\ex
\gll a ʃmː i-fːər.\\
{\PROSP} 2{\SG}.{\F}.{\OBJ} 3{\SG}.{\M}.{\SBJ}-hide.{\AOR}\\
\glt `He will hide you \textit{(fem.)}.'

\ex
\gll mani ʃmː i-fːər?\\
where 2{\SG}.{\F}.{\OBJ} 3{\SG}.{\M}.{\SBJ}-hide.{\PRET}\\
\glt `Where did he hide you \textit{(fem.)}?'

\ex
\gll mani ʃmː ala i-sːitəf?\\
where 2{\SG}.{\F}.{\OBJ} {\PROSP} 3{\SG}.{\M}.{\SBJ}-let\_in.{\AOR}\\
\glt `Where will he let you \textit{(fem.)} in?'

\clearpage

\ex
\gll i-sːitf i.\\
3{\SG}.{\M}.{\SBJ}-let\_in.{\PRET} 3{\SG}.{\M}.{\OBJ}\\
\glt `He let him in.'

\ex
\gll i-mːud i.\\
3{\SG}.{\M}.{\SBJ}-prepare.{\PRET} 3{\SG}.{\M}.{\OBJ}\\
\glt `He prepared him/it.'

\ex
\gll a sː i-sːufəɣ.\\
{\PROSP} 3{\SG}.{\M}.{\OBJ} 3{\SG}.{\M}.{\SBJ}-let\_out.{\AOR}\\
\glt `He will let him out.'

\ex
\gll mani sː i-sːitəf?\\
where 3{\SG}.{\M}.{\OBJ} 3{\SG}.{\M}.{\SBJ}-let\_in.{\PRET}\\
\glt `Where did he let him in?'

\ex
\gll mani sː ala i-fːər?\\
where 3{\SG}.{\M}.{\OBJ} {\PROSP} 3{\SG}.{\M}.{\SBJ}-hide.{\AOR}\\
\glt `Where will he hide him?'

\ex
\gll i-sːitf aməd̥ːukəl nːəs.\\
3{\SG}.{\M}.{\SBJ}-let\_in.{\PRET} friend 3{\SG}.{\GEN}\\
\glt `He let his friend in.'

\ex
\gll i-rˁːzˁ i.\\
3{\SG}.{\M}.{\SBJ}-break.{\PRET} 3{\SG}.{\M}.{\OBJ}\\
\glt `He broke him/it.'

\ex
\gll fːr-əx ʃəm(ː).\\
hide.{\PRET}-1{\SG}.{\SBJ} 2{\SG}.{\F}.{\OBJ}\\
\glt `I hid you \textit{(fem.)}.'

\ex
\gll rˁːzˁ-əx sː.\\
break.{\PRET}-1{\SG}.{\SBJ} 3{\SG}.{\M}.{\OBJ}\\
\glt `I broke him/it.'

\ex
\gll sːufɣ-əx sː.\\
let\_out.{\PRET}-1{\SG}.{\SBJ} 3{\SG}.{\M}.{\OBJ}\\
\glt `I let \textit{(past)} him out.'

\clearpage

\ex
\gll ad i-rˁːəzˁ taʒrˁa inux.\\
{\PROSP} 3{\SG}.{\M}.{\SBJ}-break.{\AOR} dish 1{\SG}.{\GEN}\\
\glt `He will break my dish.'

\ex
\gll aməd̥ːukəl inux, mani ʃmː ala i-fːər?\\
friend:{\SG} 1{\SG}.{\GEN} where 2{\SG}.{\F}.{\OBJ} {\PROSP} 3{\SG}.{\M}.{\SBJ}-hide.{\AOR}\\
\glt `My friend, where will he hide you \textit{\textit{(fem.)}}?'\ \textit{or}\ `Where will my friend hide you \textit{\textit{(fem.)}}?'

\ex
\gll mani ala sːitf-əx aməd̥ːukəl nːəs?\\
where {\PROSP} let\_in.{\AOR}-1{\SG}.{\SBJ} friend:{\SG} 3{\SG}.{\GEN}\\
\glt `Where shall I let his friend in?'

\ex
\gll mani ʃmː ala sːufɣ-əx?\\
where 2{\SG}.{\F}.{\OBJ} {\PROSP} let\_out.{\AOR}-1{\SG}.{\SBJ}\\
\glt `Where shall I let you \textit{(fem.)} out?'

\ex
\gll aməd̥ːukəl inux, i-rˁːəzˁ taʒrˁa.\\
friend:{\SG} 1{\SG}.{\GEN} 3{\SG}.{\M}.{\SBJ}-break.{\PRET} dish\\
\glt `My friend broke the dish.'

\ex
\gll i-fːr i.\\
3{\SG}.{\M}.{\SBJ}-hide.{\PRET} 3{\SG}.{\M}.{\OBJ}\\
\glt `He hid him/it.'

\ex
\gll mːud-ex sː.\\
prepare.{\PRET}-1{\SG}.{\SBJ} 3{\SG}.{\M}.{\OBJ}\\
\glt `I prepared him/it.'

\ex
\gll aməd̥ːukəl nːəs, ad i-fːər utʃu.\\
friend:{\SG} 3{\SG}.{\GEN} {\PROSP} 3{\SG}.{\M}.{\SBJ}-hide.{\AOR} couscous\\
\glt `His friend will hide the couscous.'
\end{exe}

\end{document}
